Trends of SDR in Thessaloniki

### 2023-07-15 Article.Rmd
Commit 2023-07-15 21:09

For completeness, we will provide a brief overview of the CSid process, along with the site specific thresholds.
As a reference clear sky SDR, we are using the radiation model by Haurwitz’s, adjusted for our site with a factor $a$, resulting by an iterative optimization process, as described by @Long2000 and @Reno2016.
The target of the optimization was the minimization of the function $f(a)$ (Eq.\ \ref{eq:minf}) and was accomplished with the computing function `stats::optimise` [@RCT2023], based on work by @Brent1973.
The optimization and the selection of the clear sky reference model, was performed on SDR observations for the period 2016 – 2021.
During the optimization, eight simple clear sky radiation models were tested (Daneshyar–Paltridge–Proctor, Kasten–Czeplak, Haurwitz, Berger–Duffie, Adnot–Bourges–Campana–Gicquel, Robledo-Soler, Kasten and Ineichen-Perez), with a wide range of factors. We found, that Haurwitz’s model, adjusted with the factor $a = `r signif(alpha,3)`$ has one of the lowest root mean squared error (RMSE), while correlates with large amount of our data. Thus, our clear sky reference is the Eq.\ \ref{eq:ahau}. 
The tried models are described in more details by @Reno2012 and evaluated by @Reno2016.

>>>>

For completeness, we will provide below a brief overview of the [....Csid
term is referenced above....]{.comment-start id="0" author="A N"
date="2023-07-15T20:00:52Z"}CSid algorithm[]{.comment-end id="0"}, along
with the site specific thresholds.
To calculate the reference clear sky
$\text{SDR}_\text{CSref}$ we used the [....Not visible equation....]{.comment-start id="2"
author="A N" date="2023-07-15T19:23:34Z"}${}_{}$[[]{.comment-end
id="2"}]{.insertion author="A N" date="2023-07-15T19:23:34Z"} derive by
the radiation model of @Haurwitz1945, adjusted for our site with a
factor $a$, resulted by an iterative optimization process, as described
by @Long2000 and @Reno2016.
The target of
the optimization was the minimization of the function $f(a)$ (Eq.\ \ref{eq:minf}) and
was accomplished with the computing function [\...notation
"library::function"....]{.comment-start id="2" author="A N"
date="2023-07-15T20:08:20Z"}"stats::optimise"[]{.comment-end id="2"}
of the R language [@RCT2023], with an implementation based on the work of @Brent1973. 
The optimization and the selection of the clear sky reference model, was performed on SDR observations for the period 2016 - 2021.
During the optimization, eight simple clear sky radiation models were tested (Daneshyar-Paltridge-Proctor, Kasten-Czeplak, Haurwitz, Berger-Duffie, Adnot-Bourges-Campana-Gicquel, Robledo-Soler, Kasten and Ineichen-Perez), with a wide range of factors.
These models are described in more details by @Reno2012 and evaluated by @Reno2016.
We found, that Haurwitz's model, adjusted with the factor $a = `r signif(alpha,3)`$ yields one of the lowest root mean squared errors (RMSE), [....rephrased....]{.comment-start id="3" author="A N" date="2023-07-15T20:32:50Z"}while the whole procedure, manages to characterize large amount of our data[]{.comment-end id="3"}. Thus, our clear sky reference is derived by the Eq.\ \ref{eq:ahau}.
